Preparación de datos

### 2022-07-30 production/prod_prep.Rmd
ajustes plots y tablas

#
sjmisc::frq(elsoc_long_2016_2021$in_simpat)
elsoc_long_2016_2021$in_simpat <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_simpat, 
                      label = "Sympathy for [PER/HAI/VEN] living in Chile") 
elsoc_long_2016_2021$in_simpat <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_simpat,
                       labels = c("Very little or not at all", "A little",
                                  "Somewhat","Quite a lot","A lot"))  
sjmisc::frq(elsoc_long_2016_2021$in_simpat)

#
sjmisc::frq(elsoc_long_2016_2021$in_simili)
elsoc_long_2016_2021$in_simili <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_simili, 
                      label = "Similarity between Chileans and [PER/HAI/VEN]") 
elsoc_long_2016_2021$in_simili <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_simili,
                       labels = c("Not similar", "Slightly similar", "Somewhat similar",
                                  "Quite similar", "Very similar"))
sjmisc::frq(elsoc_long_2016_2021$in_simili)

#
sjmisc::frq(elsoc_long_2016_2021$in_ansied)
elsoc_long_2016_2021$in_ansied <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_ansied, 
                      label = "Interaction anxiety with [PER/HAI/VEN].") 
elsoc_long_2016_2021$in_ansied <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_ansied,
                       labels = c("Very uncomfortable", "Uncomfortable", 
                                  "Neither comfortable nor uncomfortable",
                                  "Comfortable", "Very comfortable"))
sjmisc::frq(elsoc_long_2016_2021$in_ansied)

@@

sjmisc::frq(elsoc_long_2016_2021$in_valfam)
elsoc_long_2016_2021$in_valfam <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_valfam, 
                      label = "Family value of immigrant friends [PER/HAI/VEN]") 
sjmisc::frq(elsoc_long_2016_2021$in_valfam)

sjmisc::frq(elsoc_long_2016_2021$in_valami)
elsoc_long_2016_2021$in_valami <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_valami, 
                      label = "Friends value of immigrant friends [PER/HAI/VEN]") 
sjmisc::frq(elsoc_long_2016_2021$in_valami)

sjmisc::frq(elsoc_long_2016_2021$in_amsimb)
elsoc_long_2016_2021$in_amsimb <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_amsimb, 
                      label = "Loose of identity because of immigrants") 
sjmisc::frq(elsoc_long_2016_2021$in_amsimb)

@@

sjmisc::frq(elsoc_long_2016_2021$in_acpier)
elsoc_long_2016_2021$in_acpier <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_acpier, 
                      label = "Immigrant keeping their customs") 
sjmisc::frq(elsoc_long_2016_2021$in_acpier)

@@

sjmisc::frq(elsoc_long_2016_2021$in_amigcl)
elsoc_long_2016_2021$in_amigcl <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_amigcl, 
                      label = "Immigrants [PER/HAI/VEN] have Chilean friends") 
sjmisc::frq(elsoc_long_2016_2021$in_amigcl)

@@

# Known: Immigrant [PER/HAI/VEN]____________________________

@@

elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")

@@

# ref dejamos los 
elsoc$frien_inm_t1t4 <- 
  set_label(elsoc$frien_inm_t1t4,
            label = "Have immigrant friends (diff. t4 - t1)")

@@

# Label data____________________________________________________________________
sjlabelled::set_label(df_study1_comunas) <- 
c("Comuna",
  "Codigo Comuna",
  "Proportion of immigrant population (weighted) - CASEN 2017 - Municipality",
  "Number of immigrant population - CENSUS 2017 - Municipality",
  "Proportion of immigrant population - CENSUS 2017 - Municipality",
  "Number of immigrant population - CIT 2017 - Municipality (using census tract)",
  "Proportion of immigrant population (CIT / DEM)- CIT 2017 and INE/DEM 2017 - Communal",
  "Proportion of projected immigrant population - INE/DEM 2018 - Communal",
  "Proportion of projected immigrant population -  INE/DEM 2019 - Comunal",
  "Proportion of projected immigrant population -  INE/DEM 2020 - Comunal",
  "Proportion of immigrant population (weighted) - CASEN 2020 - Municipality",
  "Change in the proportion of the immigrant population between 2017 and 2020 - CASEN")

>>>>

#
sjmisc::frq(elsoc_long_2016_2021$in_simpat)
elsoc_long_2016_2021$in_simpat <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_simpat, 
                      label = "Sympathy for [PER/VEN] living in Chile") 
elsoc_long_2016_2021$in_simpat <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_simpat,
                       labels = c("Very little or not at all", "A little",
                                  "Somewhat","Quite a lot","A lot"))  
sjmisc::frq(elsoc_long_2016_2021$in_simpat)

#
sjmisc::frq(elsoc_long_2016_2021$in_simili)
elsoc_long_2016_2021$in_simili <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_simili, 
                      label = "Similarity between Chileans and [PER/VEN]") 
elsoc_long_2016_2021$in_simili <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_simili,
                       labels = c("Not similar", "Slightly similar", "Somewhat similar",
                                  "Quite similar", "Very similar"))
sjmisc::frq(elsoc_long_2016_2021$in_simili)

#
sjmisc::frq(elsoc_long_2016_2021$in_ansied)
elsoc_long_2016_2021$in_ansied <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_ansied, 
                      label = "Interaction anxiety with [PER/VEN].") 
elsoc_long_2016_2021$in_ansied <-
sjlabelled::set_labels(x = elsoc_long_2016_2021$in_ansied,
                       labels = c("Very uncomfortable", "Uncomfortable", 
                                  "Neither comfortable nor uncomfortable",
                                  "Comfortable", "Very comfortable"))
sjmisc::frq(elsoc_long_2016_2021$in_ansied)

@@

sjmisc::frq(elsoc_long_2016_2021$in_valfam)
elsoc_long_2016_2021$in_valfam <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_valfam, 
                      label = "Family value of migrant friends [PER/VEN]") 
sjmisc::frq(elsoc_long_2016_2021$in_valfam)

sjmisc::frq(elsoc_long_2016_2021$in_valami)
elsoc_long_2016_2021$in_valami <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_valami, 
                      label = "Friends value of migrant friends [PER/VEN]") 
sjmisc::frq(elsoc_long_2016_2021$in_valami)

sjmisc::frq(elsoc_long_2016_2021$in_amsimb)
elsoc_long_2016_2021$in_amsimb <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_amsimb, 
                      label = "Loose of identity because of migrants (reverse)")
sjmisc::frq(elsoc_long_2016_2021$in_amsimb) 
# Revert item
elsoc_long_2016_2021$in_amsimb<- 
  sjmisc::rec(elsoc_long_2016_2021$in_amsimb,rec = "rev")
sjmisc::frq(elsoc_long_2016_2021$in_amsimb) # check reverted item

@@

sjmisc::frq(elsoc_long_2016_2021$in_acpier)
elsoc_long_2016_2021$in_acpier <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_acpier, 
                      label = "Migrant keeping their customs") 
sjmisc::frq(elsoc_long_2016_2021$in_acpier)

@@

sjmisc::frq(elsoc_long_2016_2021$in_amigcl)
elsoc_long_2016_2021$in_amigcl <- 
sjlabelled::set_label(x = elsoc_long_2016_2021$in_amigcl, 
                      label = "migrants [PER/VEN] have Chilean friends") 
sjmisc::frq(elsoc_long_2016_2021$in_amigcl)

@@

# Known: Immigrant [PER/VEN]____________________________

@@

elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know migrants (diff. t4 - t1)")

@@

# ref dejamos los 
elsoc$frien_inm_t1t4 <- 
  set_label(elsoc$frien_inm_t1t4,
            label = "Have migrant friends (diff. t4 - t1)")

@@

# Label data____________________________________________________________________
sjlabelled::set_label(df_study1_comunas) <- 
c("Comuna",
  "Codigo Comuna",
  "Proportion of migrant population (weighted) - CASEN 2017 - Municipality",
  "Number of migrant population - CENSUS 2017 - Municipality",
  "Proportion of migrant population - CENSUS 2017 - Municipality",
  "Number of migrant population - CIT 2017 - Municipality (using census tract)",
  "Proportion of migrant population (CIT / DEM)- CIT 2017 and INE/DEM 2017 - Communal",
  "Proportion of projected migrant population - INE/DEM 2018 - Communal",
  "Proportion of projected migrant population -  INE/DEM 2019 - Comunal",
  "Proportion of projected migrant population -  INE/DEM 2020 - Comunal",
  "Proportion of migrant population (weighted) - CASEN 2020 - Municipality",
  "Change in the proportion of the migrant population between 2017 and 2020 - CASEN")
